---
title: "Data Transformation"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nycflights13)
library(tidyverse)
```

Letter abbreviations:  
- `<int>` stands for integers.  
- `<dbl>` stands for real numbers.  
- `<chr>` stands for character vectors.  
- `<dttm>` stands for date-times.  

```{r}
View(nycflights13::flights)
```

### 5.2.4 Exercises

1a.  
```{r}
filter(flights,arr_delay >= 120)
```

1b.
```{r}
filter(flights,dest %in% c("IAH","HOU"))

```

1c.
```{r}
filter(flights, carrier %in% c("AA","DL","UA"))
```

1d.
```{r}
filter(flights, month %in% 7:9)
```

1e.

```{r}
filter(flights, arr_delay > 120, dep_delay <= 0)
```

1f.

```{r}
filter(flights, dep_delay >= 60, (dep_delay - arr_delay > 30))
```

1g.
```{r}
filter(flights, dep_time >= 2400 | dep_time <= 600)
```

2. `<between>` is a shortcut for a<=x<=b.

```{r}
filter(flights, between(dep_time, 600 ,2400))
```

3.
```{r}
sum(is.na(flights$dep_time))
map_dbl(flights, ~ sum(is.na(.x)))
```

 Airtime, arr_delay, dep_delay and tail number have missing values.
 
 4. 
 Unsure
 
 
####5.3.1 Exercises

1. Unsure  
2. 

```{r}
arrange(flights, dep_delay)
arrange(flights, desc(dep_delay))
```
3.
```{r}
arrange(flights, air_time)
```


4.
```{r}
# Shortest
flights %>%
  arrange(air_time) %>%
  select(flight, air_time)
# Fastest
flights %>%
  arrange(-air_time) %>%
  select(flight, air_time)
```

####5.4.1 Exercises

1. 
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, starts_with("dep"), starts_with("arr"))
select_(flights, "dep_time", "dep_delay", "arr_time", "arr_delay")
```

2.
```{r}
select(flights, arr_delay,arr_delay)
```

Nothing, only returns once.

3.

```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```
Unsure why helpful.

4.

```{r}

select(flights, contains("TIME"))
```

Unsure.















